Protocol

### 2024-08-14 pages/protocol.qmd
docs(quarto): minor amendment to title and a little content for the protocol page

TODO: This page summarises the method from the protocol.

>>>>

<!-- TODO: Write out a summary here -->

The protocol for this work is summarised in the diagram below and archived on Zenodo:

> Heather, A., Monks, T., Harper, A., Mustafee, N., & Mayne, A. (2024). Protocol for assessing the computational reproducibility of discrete-event simulation models on STARS. Zenodo. <https://doi.org/10.5281/zenodo.12179846>.

![Workflow for STARS work package 1](../images/stars_wp1_workflow.png)
